Extending Morphological Chains with Supervised Learning and Cross-Language Features

### 2015-12-10 paper/paper.tex
paper

\begin{center}
    \begin{tabular}{ | l | l | l | l | l |}
    \hline
    Language & Method & Precision & Recall & F1 \\ \hline
      & Narasimhan & 0.807 & 0.722 & 0.762 \\ 
    & Unsupervised & -  & - & - \\ 
    English & Semi-supervised & - & - & - \\ 
     & Two language unsupervised & - & - & - \\ 
     & Two language semi-supervised & - & - & - \\ \hline
     & Narasimhan & 0.743 & 0.520 & 0.612 \\ 
    & Unsupervised & - & - & - \\ 
    Turkish & Semi-supervised & - & - & -  \\ 
     & Two language unsupervised  & - & - & -  \\ 
     & Two language semi-supervised  & - & - & -  \\ \hline
    \end{tabular}
\end{center}

\begin{center}
    \begin{tabular}{ | l | l | l | l | l | l |}
    \hline
    Language & \multicolumn{2}{|c|}{\textbf{Correct Segmentations}} & \multicolumn{3}{|c|}{\textbf{Incorrect Segmentations}}\\ \hline
     & Word & Segmentation & Word & Predicted & Correct\\ \hline
    & 'suburbanite' & 'suburb/an/ite' & 'provokingly' & 'provok/ing/ly' & 'provoking/ly'  \\ 
    'buffeted' & 'buffeted' & -  & - & - & -\\ 
    "ewers'" &  "ewer/s/'" & - & - & - & -\\ 
    'yowling' & 'yowl/ing' & - & - & -& - \\ 
     & Two language semi-supervised & - & - & - & -\\ \hline
     & Narasimhan & 0.743 & 0.520 & 0.612 & -\\ 
    & Unsupervised & - & - & - & -\\ 
    Turkish & Semi-supervised & - & - & -  & -\\ 
     & Two language unsupervised  & - & - & -  & -\\ 
     & Two language semi-supervised  & - & - & -  & -\\ \hline
    \end{tabular}
\end{center}

>>>>

\begin{table*}
    \begin{center}
        \begin{tabular}{ | l | l | l | l | l |}
            \hline
            Language & Method & Precision & Recall & F1 \\ \hline
                     & Narasimhan & 0.807 & 0.722 & 0.762 \\ 
                     & Unsupervised & -  & - & - \\ 
            English & Semi-supervised & - & - & - \\ 
                    & Two language unsupervised & - & - & - \\ 
                    & Two language semi-supervised & - & - & - \\ \hline
                    & Narasimhan & 0.743 & 0.520 & 0.612 \\ 
                    & Unsupervised & - & - & - \\ 
            Turkish & Semi-supervised & - & - & -  \\ 
                    & Two language unsupervised  & - & - & -  \\ 
                    & Two language semi-supervised  & - & - & -  \\ \hline
        \end{tabular}
        \caption{Results 'n shit TODO}
    \end{center}
\end{table*}

\begin{table*}
    \begin{center}
        \begin{tabular}{ | l | l | l | l | l | l |}
            \hline
            Language & \multicolumn{2}{|c|}{\textbf{Correct Segmentations}} & \multicolumn{3}{|c|}{\textbf{Incorrect Segmentations}}\\ \hline
                     & Word & Segmentation & Word & Predicted & Correct\\ \hline
            English & suburbanite & suburb/an/ite & provokingly & provok/ing/ly & provoking/ly  \\ 
                    & buffeted & buffeted & -  & - & -\\ 
                    & ewers' &  ewer/s/' & - & - & -\\ 
                    & yowling & yowl/ing & - & -& - \\ 
                    & Two language semi-supervised & - & - & - & -\\ \hline
                    & Narasimhan & 0.743 & 0.520 & 0.612 & -\\ 
            Turkish & Unsupervised & - & - & - & -\\ 
                    & Semi-supervised & - & - & -  & -\\ 
                    & Two language unsupervised  & - & - & -  & -\\ \hline
                    & - & - & - & -  & -\\ 
                    & - & - & - & -  & -\\ 
    English (dual-language) & - & - & - & -  & -\\ 
                    & - & - & - & -  & -\\ 
                    & - & - & - & -  & -\\ \hline
                \end{tabular}
        \caption{Results 'n shit TODO}
    \end{center}
\end{table*}
